Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2021-11-25 Scripts/Initial_Analysis.Rmd
Nvm.. Back to showing the mean

  boxplot_data <- Eme_Res %>%
    # Get the order of boxes
    filter(tresh == tresh_list[i],
           !is.na(un_sub_region)) %>%
    group_by(un_sub_region) %>%
    summarise(order = median(emerging_yr),
              n_eezs = length(unique(sf_eez_name))) %>%
    # Get the rest of the data
    left_join(Eme_Res) %>%
    filter(tresh == tresh_list[i],
           !is.na(un_sub_region)) %>%
    mutate(un_sub_region = ifelse(str_detect(un_sub_region,"Latin"),"Ltn. Ame. and\nthe Car.",
                                  ifelse(str_detect(un_sub_region,"Australia"),"Aus. and New Z.",
                                         ifelse(str_detect(un_sub_region,"Sub-Saharan"),"Sub-Saharan\nAfrica",
                                                paste(un_sub_region)))
    ),
    # For number labels
    un_sub_region = paste(un_sub_region," (n = ",n_eezs,")",sep="")
    )

@@

  ggsave("mean_boxplot.png",boxplot,width = 10)

@@

>>>>

  boxplot_data <- Eme_Res %>%
    # Get the order of boxes
    filter(tresh == tresh_list[i],
           !is.na(un_sub_region)) %>%
    group_by(un_sub_region) %>%
    summarise(order = mean(emerging_yr),
              n_eezs = length(unique(sf_eez_name))) %>%
    # Get the rest of the data
    left_join(Eme_Res) %>%
    filter(tresh == tresh_list[i],
           !is.na(un_sub_region)) %>%
    mutate(un_sub_region = ifelse(str_detect(un_sub_region,"Latin"),"Ltn. Ame. and\nthe Car.",
                                  ifelse(str_detect(un_sub_region,"Australia"),"Aus. and New Z.",
                                         ifelse(str_detect(un_sub_region,"Sub-Saharan"),"Sub-Saharan\nAfrica",
                                                paste(un_sub_region)))
    ),
    # For number labels
    un_sub_region = paste(un_sub_region," (n = ",n_eezs,")",sep="")
    )

@@

  # ggsave("mean_boxplot.png",boxplot,width = 10)

@@

###### Lat Am Figure 3 for supplements

World_map_part <- World_map_nemer %>% 
    filter(
      variable == "value"
    )

  # ToE Map 
  toe_map_data <- World_eez_sf %>% 
    left_join(Eez_d_hist,
              by = "eezid") %>% 
    filter(metric == "mean_yr")%>% 
    sf::st_transform(crs = "+proj=eck4")

  no_toe_eez <- World_eez_sf %>% 
    filter(eez_name %in% Neighbours$eez_name, # Filter EEZs without Transboundary spp
           !eez_name %in% toe_map_data$eez_name) %>%  # Filter EEZs with ToE stocks
    sf::st_transform(crs = "+proj=eck4")

  no_toe_land <- World_map %>% 
    filter(name %in% Neighbours$eez_name, # Filter EEZs without Transboundary spp
           !name %in% World_map_part$name)%>% 
    sf::st_transform(crs = "+proj=eck4")

lat_ammap <- ggplot(toe_map_data) +
    geom_sf(
      aes(
        fill = reverse #original map
        # fill = value
      ),
      color =  "white",
      size = 0.1
    ) +
    # Inlcude the participation of species
    geom_sf(data = World_map_part,
            # aes(fill = participation+2000), #original map
            aes(fill = participation, 
                color = participation),
            # color =  "white",
            size = 0.1
    ) +
    # grey maps
    # ggplot() +
    geom_sf(data = grey_land, aes(), fill = "grey50", 
            # color =  "white",
            size = 0.1) +
    # geom_sf(data = grey_eez, aes(), fill = "white", color =  "grey50",size = 0.1) +
    geom_sf(data = no_toe_eez, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    geom_sf(data = no_toe_land, aes(), fill = "lightblue", color =  "white",size = 0.1) +
  coord_sf(xlim = c(-9000000,-5000000),ylim = c(1000000, 4000000)) + 
  facet_wrap(~tresh) +
  scale_colour_viridis("",
                         limits = c(2000,2100),
                         breaks = seq(2000,2100,25),
                         # labels = c("","","","",""),
                         direction = 1
    ) +
    scale_fill_viridis("",
                         limits = c(2000,2100),
                         breaks = seq(2000,2100,25),
                         # labels = c("","","","",""),
                         direction = 1
    ) +
    my_ggtheme_m(map_type = "regional",leg_pos = "")

ggsave("lat_am_map.png",
       lat_ammap,
       height = 5,
       width = 6)

###### SP Islands Figure 3 for supplements

  # Value Map
  spi_map_part <- World_map_nemer %>% 
    filter(
      # tresh ==  tresh_list[i],
      variable == "value"
    ) %>% 
  sf::st_transform(crs = 3832)

  # ToE Map 
  spi_toe_map_data <- World_eez_sf %>% 
    left_join(Eez_d_hist,
              by = "eezid") %>% 
    filter(#tresh == tresh_list[i],
           metric == "mean_yr")%>% 
    sf::st_transform(crs = 3832)

  # Map with countries without ToE
  spi_no_toe_eez <- World_eez_sf %>% 
    filter(eez_name %in% Neighbours$eez_name, # Filter EEZs without Transboundary spp
           !eez_name %in% toe_map_data$eez_name) %>%  # Filter EEZs with ToE stocks
    sf::st_transform(crs = 3832)

  spi_no_toe_land <- World_map %>% 
    filter(name %in% Neighbours$eez_name, # Filter EEZs without Transboundary spp
           !name %in% World_map_part$name)%>% 
    sf::st_transform(crs = 3832) # Filter EEZs with ToE stocks

  sp_map <-  ggplot(spi_toe_map_data) +
    geom_sf(
      aes(
        fill = reverse #original map
        # fill = value
      ),
      color =  "white",
      size = 0.1
    ) +
    # Inlcude the participation of species
    geom_sf(data = spi_map_part,
            # aes(fill = participation+2000), #original map
            aes(fill = participation, 
                color = participation),
            # color =  "white",
            size = 0.1
    ) +
    # grey maps
    geom_sf(data = spi_no_toe_eez, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    geom_sf(data = spi_no_toe_land, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    coord_sf(xlim = c(9500000,1000000),ylim = c(-3500000, 1900000)) + 
    facet_wrap(~tresh) +
    scale_colour_viridis("",
                         limits = c(2000,2100),
                         breaks = seq(2000,2100,25),
                         # labels = c("","","","",""),
                         direction = 1
    ) +
    scale_fill_viridis("",
                         limits = c(2000,2100),
                         breaks = seq(2000,2100,25),
                         # labels = c("","","","",""),
                         direction = 1
    ) +
    my_ggtheme_m(map_type = "regional",leg_pos = "bottom") +
    theme(legend.key.width = unit(3, "line"))
